### 2017-07-30 ms/results.tex
old version of eq 2 in 4, of 54-55

\centerline{$^2$School of Mathematical Sciences}
%\vskip-7pt
\centerline{Tel Aviv University}
%\vskip-7pt
\centerline{Tel Aviv, Israel 69978}
%\vskip-7pt
\centerline{uril@tauex.tau.ac.il}
\vfil
\centerline{July 27, 2017, v.1}

@@

Therefore, the frequency of phenotype $A$ after one generation is given by the recursion equation
$$
x' = \rho  {w_A\over \overline w} x + (1-\rho) x
.\eqno(2)$$
which can be rewritten as 
$$
x' = 
x \cdot \Bigl(1 - \rho + \rho {w_A \over w_A x + w_B (1-x)}\Bigr) = 
x \cdot \Bigl(1 + \rho (1-x) {w_A-w_B \over \overline w} \Bigr)
.\eqno(4)$$

@@

 Suppose that the vertical transmission rate is determined by a genetic locus with two possible alleles $m$ and $M$. Let the vertical transmission rates determined by $m$ and $M$ be $\rho$ and $P$, respectively. Thus there are four pheno-genotypes $mA$, $mB$, $MA$, and $MB$ whose frequencies at a given generation are denoted by $x_1$, $x_2$, $x_3$, and $x_4$, respectively. As the fitness values are determined by the two phenotypes $A$ and $B$, and the modifier locus is selectively neutral, we have the following table.
 $$\matrix{
 \hbox{\tenrm pheno-genotype}&mA&mB&MA&MB\cr\noalign{\smallskip}
 \hbox{\tenrm frequency}&x_1&x_2&x_3&x_4\cr\noalign{\smallskip}
 \hbox{\tenrm fitness}&w_A&w_B&w_A&w_B\cr\noalign{\smallskip}
 \hbox{\tenrm vertical transmission rate}&\rho&\rho&P&P\cr}\eqno(53)$$
 Following the rationale leading to equation (2), the pheno-genotype frequencies after selection are
 $$\eqalign{
 x_1^S = {w_A \over \overline w}x_1\cr
 x_2^S = {w_B \over \overline w}x_2\cr
 x_3^S = {w_A \over \overline w}x_3\cr
x_4^S = {w_B \over \overline w}x_4,
}\eqno(54)$$
with the mean fitness $\overline w$ given by $\overline w=\sum_{i=1}^{4}{x_i^S}$,
and the frequencies of the phone-genotypes at the next generations are
 $$\eqalign{
 x'_1 &= \rho x_1^S + (1-\rho)(x_1^S + x_2^S)(x_1+x_3)\cr
 x'_2 &= \rho x_2^S + (1-\rho)(x_1^S + x_2^S)(x_2+x_4)\cr 
 x'_3 &= P x_3^S + (1-P)(x_3^S+x_4^S)(x_1+x_3)\cr
 x'_4 &= P x_4^S + (1-P)(x_3^S+x_4^S)(x_2+x_4), 
}\eqno(55)$$

>>>>

\centerline{$^2$School of Mathematical Sciences}
%\vskip-7pt
\centerline{Tel Aviv University}
%\vskip-7pt
\centerline{Tel Aviv, Israel 69978}
%\vskip-7pt
\centerline{uril@tauex.tau.ac.il}
\vfil
\centerline{July 27, 2017, v.2}

@@

Therefore, the change in frequency of phenotype $A$ after one generation due to selection ($ {w_A\over \overline w}$) and vertical ($\rho$) and oblique ($1-\rho$) transmission is given by the recursion equation
$$
x' = \rho  {w_A\over \overline w} x + (1-\rho) x
,\eqno(2)$$
which can be rewritten as 
$$\eqalign{
x' = 
\bigl(1-x\bigr) {w_A\over \overline w} \bigl((1-\rho)x + \rho\bigr) + \bigl(1-x\bigr) {w_B\over \overline w} \bigl(1-\rho\bigr)x = \cr
x \cdot \Bigl(1 - \rho + \rho {w_A \over \overline w}\Bigr) = \cr
x \cdot \Bigl(1 + \rho \bigl(1-x\bigr) {w_A-w_B \over \overline w} \Bigr)
.}\eqno(4)$$

@@

 Suppose that the vertical transmission rate is determined by a genetic locus with two possible alleles $m$ and $M$. Let the vertical transmission rates determined by $m$ and $M$ be $\rho$ and $P$, respectively. Thus there are four pheno-genotypes $mA$, $mB$, $MA$, and $MB$ whose frequencies at a given generation are denoted by $x_1$, $x_2$, $x_3$, and $x_4$, respectively. As the fitness values are determined by the two phenotypes $A$ and $B$, and the modifier locus is selectively neutral, we have the following table.
 $$\matrix{
 \hbox{\tenrm pheno-genotype}&mA&mB&MA&MB\cr\noalign{\smallskip}
 \hbox{\tenrm frequency}&x_1&x_2&x_3&x_4\cr\noalign{\smallskip}
 \hbox{\tenrm fitness}&w_A&w_B&w_A&w_B\cr\noalign{\smallskip}
 \hbox{\tenrm vertical transmission rate}&\rho&\rho&P&P\cr}\eqno(53)$$
 Following the rationale leading to equation (2), the pheno-genotype frequencies after one generations are described by
 $$\eqalign{
 \overline w x_1' = w_A x_1\bigr[(1-\rho)(x_1+x_3)+\rho \bigl] + w_B x_2(1-\rho)(x_1+x_3)\cr
 \overline w x_2' = w_A x_1(1-\rho)(x_2+x_4) + w_B x_2 \bigl[(1-\rho)(x_2+x_4) + \rho \bigr]\cr
 \overline w x_3' = w_A x_2\bigr[(1-P)(x_1+x_3)+P \bigl] + w_B x_4(1-\rho)(x_1+x_3)\cr
 \overline w x_2' = w_A x_3(1-P)(x_2+x_4) + w_B x_4 \bigl[(1-P)(x_2+x_4) + P \bigr]
}\eqno(54)$$
with the mean fitness $\overline w$ given by
$$\overline w=w_A (x_1+x_3) + w_B (x_2+x_4).\eqno(55)$$
